Capstone Movielens Report

### 2025-01-29 reports/capstone-movielens-report.Rmd
Rmd Report updated.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

>>>>

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
#bibliography: [references.bib]
#link-citations: true
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
vignette: >
  %\VignetteIndexEntry{RMarkdown Citations - Alphabetic Style}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=TRUE}
library(RefManageR)
bib <- ReadBib(system.file("Bib", "references.bib", 
                           package = "RefManageR"), check = FALSE)
BibOptions(check.entries = FALSE, style = "markdown", bib.style = "alphabetic", cite.style = 'alphabetic')
knitr::opts_chunk$set(echo = TRUE)
```

@@

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the^[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)] requirements, we will evaluate the RMSE score^[Rafael A. Irizarry: Introduction to Data Science, Part II, Section 23.2: Loss function]:

Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563^[R: A Language and Environment for Statistical Computing, Section 33.6.1 Matrix Factorization, @R-base]).

@@

## Refs

[Rafael A. Irizarry. Introduction to Data Science, Part II](https://rafalab.dfci.harvard.edu/dsbook-part-2/)

1.23.2 [Section 23.2: Loss function](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function)

[Töscher, A., Jahrer, M., & Bell, R. M. (2009). The BigChaos Solution to the Netflix Grand Prize](https://www.asc.ohio-state.edu/statistics/statgen/joul_aut2009/BigChaos.pdf)
